### 2019-07-26 thesis.tex
*** empty log message ***

\chapter{Applications to astrophysical plasmas}
\label{appD}
On Earth, the plasma is considered an exotic state of matter, associated to the
glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
laboratories, and the promise of cleaner and practically inexhaustible energy
source once we have controlled and energetically efficient thermonuclear fusion
\cite{bell}. Naturally occurring plasmas in our everyday life are rare, restricted
to the occurrence of lightning during storms, flames, and the beautiful auroras
that take place at high latitudes. In the space, however, the situation is the
opposite. Starting in the outer layers of Earth's atmosphere, passing through the
solar wind in the interplanetary space, to the stellar interiors and atmospheres,
accretion disks, and molecular clouds it is estimated that something around
$99 \sim 99.9\%$ of the observable matter in the universe is in the plasma state
\cite{may}. Therefore, the study of the physics of plasma processes is a
fundamental branch of astrophysics\cite{tsypa}.

The analysis presented in this doctoral thesis has relevant contributions in the
study of the combined action of nonlinear kinetic instabilities and collisional
processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
profile under consideration might be considered quite idealized, the physical
processes that are being addressed have fundamental character - the plasma waves
under consideration and the particle interactions are inherent to any plasma.
The underlying nature of these processes means that they might impact the plasma
dynamics at different astrophysical environments and also in laboratory plasmas.
Laboratory plasmas, however, are usually constrained by very specific conditions
that are unique to each experiment. This specificity makes the analysis in the
experimental context counter productive. A more broad approach is to compare our
theoretical results with plasma phenomena that are independent of imposed laboratory
conditions: astrophysical plasmas.

 In this appendix, we will make a brief revision on solar
physics, pointing out the phenomena that are associated with our model.

%Plasma is a gas in which the atoms -or molecules- are in an ionized state.
% In such condition, long-range electric and magnetic forces determine the
% interactions of the charged particles. This coupling between the variations
% in the electric and magnetic fields and the motion of ions and electrons
% is the cause of the wide variety of oscillatory processes that characterize
% the plasma dynamics\cite{tsytotp}.

% In this thesis, we present a theoretical model for the inclusion of single
% particle fluctuations and collisional processes related to electrostatic
% oscillation in rarefied, unmagnetized, non-relativistic and fully ionized
% plasmas.

% \section{Kinetic processes in astrophysical plasmas}
% \label{sec:astro-plasma}

>>>>

\chapter{Applications to astrophysical plasmas}
\label{appD}
% On Earth, the plasma is considered an exotic state of matter, associated to the
% glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
% laboratories, and the promise of cleaner and practically inexhaustible energy
% source once we have controlled and energetically efficient thermonuclear fusion
% \cite{bell}. Naturally occurring plasmas in our everyday life are rare, restricted
% to the occurrence of lightning during storms, flames, and the beautiful auroras
% that take place at high latitudes. In the space, however, the situation is the
% opposite. Starting in the outer layers of Earth's atmosphere, passing through the
% solar wind in the interplanetary space, to the stellar interiors and atmospheres,
% accretion disks, and molecular clouds it is estimated that something around
% $99 \sim 99.9\%$ of the observable matter in the universe is in the plasma state
% \cite{may}. Therefore, the study of the physics of plasma processes is a
% fundamental branch of astrophysics\cite{tsypa}.

The analysis presented in this doctoral thesis has relevant contributions in the
study of the combined action of nonlinear kinetic instabilities and collisional
processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
profile under consideration might be considered quite idealized, the physical
processes that are being addressed have fundamental character - the plasma waves
under consideration and the particle interactions are inherent to any plasma.
The underlying nature of these processes means that they might impact the plasma
dynamics at different astrophysical environments and also in laboratory plasmas.
Laboratory plasmas, however, are usually constrained by very specific conditions
that are unique to each experiment. This specificity makes the analysis in the
experimental context counter productive. A more broad approach was then to compare
our theoretical results with phenomena observed in the naturally occurring space
plasma\footnote{In the literature, the term ``astrophysical plasma'' is sometimes
  used to refer to the plasma observed outside the solar system, while ``space
  plasma'' is used to account for the plasma in our interplanetary space. In this
  text, however, both terms are being used as synonyms.}. The accessibility to
direct, in situ measurements, highly resolved remote sensing and high-resolution
spectroscopy make of the solar plasma the right choice for our analysis.

% In order to offer a deeper insight on the solar phenomena 
% In this appendix, we make a brief description of the solar processes that are
% being addressed by our theory.

\section{}
\label{sec:solar-physics}
The Sun is a G2 main-sequence star. From the stellar astrophysics point
of view, it is considered ordinary, without any unique property that could
differentiate it from other main-sequence stars; except for the fact that
it is remarkably close to us. These two facts make the Sun a perfect model
of study, not only for stellar evolution theorists but also for plasma
physicists.
